A Logic-Based Framework for Digital Signal Processing

### 2008-06-05 paper/paper.tex

\usepackage{url}
\urldef{\mails}\path|{david.pastor, yves.raimond, mark.sandler}@elec.qmul.ac.uk|

@@

\author{David Pastor\and Yves Raimond\and Mark Sandler}

@@

\begin{itemize}
 \item Allowing workflows design
 \item Providing an interface to interact with other related systems and applications
 \item Featuring an unified, flexible and understandable front-end
 \item Providing a open-development platform
 \item Management of shareable data semantically labelled
 \item Relying on a logic framework which allow us to use and provide new capabilities than traditional procedural implementations: declarative meaning of , reasoning, inferencing, computations as queries, 
\end{itemize}

@@

@@

In section \ref{sec:tasks} we have seen how tasks are strongly characterized by their input/output relationship. The system require to define datatypes that guarantee the correct input and output matching. We identify these datatypes by analysing the differnt tasks explained. We also want to look at the Music Ontology specification \cite{mo} as a ``web ontology'' description of music-related concepts including audio analysis terminology. We distinguish the following datatypes:

\begin{itemize}
Mercury
Define datatypes
\end{itemize}

We implement these datatypes in SWI-Prolog as functors (name/arity) that bind together the attributes of a concept (e.g. signal(Channels, SampleRate, Length, [DataIdPerChannel])). These datatypes (with the disadvantage of being a non-flexible model) can be interpreted to any module guaranteeing the correct instantation pattern of the predicates and ensuring a valid execution.

@@

The following example shows how a decoded audio file can be easily represented by the data identifiers that make easy to work with such a big sequence of data.
\begin{verbatim}
:-decode('../myfile.*', Signal).
Signal = signal(2, 44100, 1200000, ['__data_0', '__data_1']).

:-data_out('__data_0', '../myfilech1').
:-data_out('__data_1', '../mufilech2').

:-frame(signal(2, 44100, 1200000, ['__data_0', '__data_1']), 200, 5, frame(Ch, Sr, L, [Ch1D, Ch2D])),
data_to_list(Ch1D, List), length(List, Llen).
Ch1D = '__data_2'
List = [6.45, 4.56, 3.23, 9.78, 3.26]
Llen = 5
\end{verbatim}

>>>>

\usepackage{url}
\urldef{\mails}\path|{david.pastor, yves.raimond, samer.abdallah, mark.sandler}@elec.qmul.ac.uk|

@@

\author{David Pastor\and Yves Raimond\and Samer Abdallah\and Mark Sandler}

@@

\begin{itemize}
 \item Allowing workflows design
 \item Providing an interface to interact with other related systems and applications
 \item Featuring an unified, flexible, interactive and understandable front-end
 \item Providing an open-development platform
 \item Management of shareable data semantically labelled
 \item Enhancing traditional procedural implementations by building a logic-based framework of declarative nature allowing reasoning and inferencing.
\end{itemize}

@@

This layout allow us to wrap fast and efficient implementations of algorithms (in some imperative language) to provide predicates that determine the relationship between defined types (as black box computation) giving a ``functional programming'' view of the system preserving computational efficiency. This functional programming approach (which allow us to create workflows as rules with a procedural meaning) is motivated by the advantages of functional languages like Haskell \cite{haskell} that present a semantically oriented view of computations instead of a machine-oriented one. There are also several works that develop such a typed-functional language on a logic framework like lambda-Prolog \cite{lambda} or Mercury \cite{mercury}. However, our approach results to be more suitable to develop an open platform for research and development. External engines based on open source APIs provide faster computations than any functional or logic/strong-typed language and a suitable developers interface. Furthermore, SWI-Prolog features a very powerful, interactive and flexible front-end which is also a requirement for the proposed system.

@@

In section \ref{sec:tasks} we have seen how tasks are strongly characterized by their input/output relationship. The system requires datatypes that guarantee the correct input and output matching. We identify these datatypes by analysing the tasks classification. We also want to look at the Music Ontology specification \cite{mo} as a ``web ontology'' description of music-related concepts including audio analysis terminology. We distinguish the following datatypes:

\begin{itemize}
 \item signal: this type represents an audio signal in a physical timeline. T
\end{itemize}

We implement these datatypes in SWI-Prolog as functors (name/arity) that bind together the attributes of a concept (e.g. signal(Channels, SampleRate, Length, [DataIdPerChannel])). These datatypes (with the disadvantage of being a non-flexible model) can be interpreted by any module guaranteeing the correct instantation pattern of the predicates and ensuring a valid execution.

@@

The following example shows how a decoded audio file can be easily represented by the data identifiers that make easy to work with such a big sequence of data.
\begin{verbatim}
?-decode('../myfile.*', Signal).
Signal = signal(2, 44100, 1200000, ['__data_0', '__data_1']).

?-data_out('__data_0', '../myfilech1').
?-data_out('__data_1', '../mufilech2').

?-get_frame(signal(2, 44100, 1200000, ['__data_0', '__data_1']), 200, 5,
frame(Ch, Sr, L, [Ch1D, Ch2D])),
data_to_list(Ch1D, List), length(List, Llen).
Ch1D = '__data_2'
List = [6.45, 4.56, 3.23, 9.78, 3.26]
Llen = 5
\end{verbatim}
